\cvsection{Posters \& Presentations}
\cvsubsection{Invited Presentations}


\begin{sloppypar}
\begin{small}

\hangindent=3.5em
\hangafter=1
\textbf{2023} - \textit{Affective \& Brain Sciences Lab, Northeastern University}. Emotions, Self-Regulation Use, and Forecasting Using Dynamic, Feature-Rich Stimuli.\cvcolortag{Presenter}{tagline} \newline

\hangindent=3.5em
\hangafter=1
\textbf{2023} - \textit{March Lab, Florida State University}. Fear Factor: Emotions and Self-Regulation in a Threatening, Quasi-Naturalistic Setting. \cvcolortag{Presenter}{tagline} \newline

\hangindent=3.5em
\hangafter=1
\textbf{2021} - \textit{Fundamentals of the Adolescent Brain Lab, Yale University}. Neural representations of affective information across developmental contexts. \cvcolortag{Presenter}{tagline} \\

\end{small}
\end{sloppypar}

\cvsubsection{Symposia \& Seminars}

\hangindent=3.5em
\hangafter=1
\textbf{Mitchell, W.J.}, Helion, C., Satpute, A.B., Nook, E.C., \& Cosme, D.J., (2022). Contextualizing Emotion – Influences of Context on Affective Representation, Experience and Regulation. \textit{Annual Conference of the American Psychological Association in Minneapolis, MN}.\cvcolortag{Organizer}{name}\cvcolortag{Presenter}{tagline}\\

\hangindent=3.5em
\hangafter=1
\textbf{Mitchell, W.J.}, Tepfer, L. J., Henninger, N. M., Perlman, S. B., Murty, V. P., \& Helion, C. (2022). Neurodevelopmental differences in affective representations between adults and children. \textit{Annual Decision Neuroscience Symposium in Philadelphia, PA}.\cvcolortag{Presenter}{tagline}\\

\hangindent=3.5em
\hangafter=1
\textbf{Mitchell, W.J.}, Stasiak, J., Gregory, D., Reisman, S., Murty, V., \& Helion, C. (2020). When We Regulate At Eastern State: Regulation
Beyond the Lab. \textit{Maladaptive Motivational Behavior Seminar Series in Philadelphia, PA}.\cvcolortag{Presenter}{tagline} \\

\cvsubsection{Selected Poster Presentations}

\hangindent=3.5em
\hangafter=1
\textbf{Mitchell, W.J.}, Stasiak, J., Cliver, K., Martinez, S., Gregory, D., Reisman, S., Murty, V., \& Helion, C. (2024). High-Intensity, Dynamic Stimuli Complicate Emotion Regulation Strategy Usage. \textit{Annual Convention of the Society for Personality and Social Psychology in San Diego, CA}.\cvcolortag{Presenter}{tagline}

\hangindent=3.5em
\hangafter=1
\textbf{Mitchell, W.J.}, Stasiak, J., Cliver, K., Martinez, S., Gregory, D., Reisman, S., Murty, V., \& Helion, C. (2023). Emotion Regulation Strategy Usage in a Quasi-Naturalistic Context. \textit{Annual Convention of the Society for Affective Science in Long Beach, CA}.\cvcolortag{Presenter}{tagline}

\hangindent=3.5em
\hangafter=1
\textbf{Mitchell, W.J.}, Tepfer, L.J., Henninger, N., Perlman, S.B., Murty, V., \& Helion, C. (2022). Do You Feel How I Feel?: Developmental
Differences in Affective Neural Representations. \textit{Annual Flux convention in Paris, FR}.\cvcolortag{Presenter}{tagline} \href{https://www.youtube.com/watch?v=V6gwc6Ss1kg}{\cvcolortag{Video}{headingrule}}

\hangindent=3.5em
\hangafter=1
\textbf{Mitchell, W.J.}, Stasiak, J., Gregory, D., Reisman, S., Murty, V., \& Helion, C. (2022). Emotional Intensity Influences Prediction but
Not Action in Emotion Regulation. \textit{Annual Convention of the Society for Affective Science}.\cvcolortag{Presenter}{tagline}\href{https://www.youtube.com/watch?v=eVhc9k2PZ8k}{\cvcolortag{Video}{headingrule}}

\hangindent=3.5em
\hangafter=1
\textbf{Mitchell, W.J.}, Stasiak, J., Gregory, D., Reisman, S., Murty, V., \& Helion, C. (2022). Emotional Intensity Influences Prediction but
Not Action in Emotion Regulation. \textit{Annual Convention of the Society for Personality and Social Psychology}.\cvcolortag{Presenter}{tagline}
\href{https://www.youtube.com/watch?v=imL2EMoqRWs}{\cvcolortag{Video}{headingrule}}

\hangindent=3.5em
\hangafter=1
\textbf{Mitchell, W.J.}, Tepfer, L.J., Henninger, N., Murty, V., Helion, C., \& Perlman, S.B. (2021). Do You Feel How I Feel?: Developmental
Differences in Affective Neural Representations. \textit{Annual Meeting of the Social Affective Neuroscience Conference}.\cvcolortag{Presenter}{tagline} \href{https://youtu.be/ucwGXVEUDuA}{\cvcolortag{Video}{headingrule}}

\hangindent=3.5em
\hangafter=1
\textbf{Mitchell, W.J.}, Tepfer, L.J., Henninger, N., Murty, V., Helion, C., \& Perlman, S.B. (2021). Do You Feel What I Feel?: Developmental
Differences in Emotion Representation. \textit{Annual Meeting of the Society for Personality and Social Psychology Emotion Pre-Conference}.\cvcolortag{Presenter}{tagline}\href{https://youtu.be/X6H7pUEdow8}{\cvcolortag{Video}{headingrule}}

\hangindent=3.5em
\hangafter=1
\textbf{Mitchell, W.J.}, Stasiak, J., Gregory, D., Reisman, S., Murty, V., \& Helion, C. (2021). Fear and Loathing in Eastern State Penitentiary:
Emotion Regulation in a Quasi-Naturalistic Setting. \textit{Annual Meeting of the Society for Personality and Social Psychology}.\cvcolortag{Presenter}{tagline}